---
title: "exercise3"
author: "Spencer Lee"
date: "2022-12-08"
output: github_document ## change to github_document at the end
---

```{r setup, include=FALSE}
library(tidyr)
library(ggplot2)
library(palmerpenguins)
library(gapminder)
library(purrr)
library(broom)
library(dplyr)
```

# Column of model objects
I will be performing data analysis on the gapminder dataset, where I'll be analyzing the relationship life expectancy and year. We will use the linear. We will be extracting the 2 coefficients from each lm, where each coefficient represents the slope and y-intercept of the model. This can be fitted onto a plot and/or analyzed to determine the general trend overtime. For example, we saw the USA have the coefficients of 1.841692e-01	and -2.910845e+02, which represent the slope and y-intercept respectively. This demonstrates that the life expectancy in the US is increasing overtime, and the y-intercept is -2.9 years. Although the y-intercept is negative (at year 0), this part of the linear model is out of range, where data in included from 1960 to 2005.

```{r}
# Cleaning up gapinder
gap <- gapminder %>%
  as_tibble()

# Task 1 and Task 2
# Map each model to the gapminder data, we're using lifeExp and year in this case.
list_m <- gap %>%
  group_by(country) %>%
  nest() %>%
  mutate(model = map(data, ~ lm(lifeExp ~ year, data = .)))

# Task 3 intermediate table
list_m

# Task 4
# Extracting coefficients from each lm and unnesting the calculations
list_m_pull <- list_m %>% 
    mutate(lm_coefficients = map(model, coef), 
           )
list_m_pull

list_un <- list_m_pull %>%
    unnest(lm_coefficients)
list_un


```


# Part 2: Plotting fitted lm on each country

Here we're going to be fitting the lm model of each continent on a scatter plot differentiated by different colours. We can see that overtime, the general life expectancy in each continent is increasing at the same rate. Interestingly Oceania has the highest life expectancy. We can also see the the linear regression line fitted to each continents life expectancy and year fall roughly between the scatter points at each year, indicating the the linear model is fit correctly and appropriately (linearity).
```{r}
plot <- gapminder %>%
  group_by(continent, year) %>%
  ggplot(aes(x = year, y = lifeExp, color = continent)) +
  #  facet_wrap(c("Canada", "United Kingdom"), scales = "free") +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
plot
```